---
title: "Going beyond the defaults with bakR"
author: "Isaac Vock"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Further-Analyses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(6, 4)
)
```


## Introduction

Welcome! This vignette discusses an exciting hodge-podge of additional analyses that can be done with bakR. The assumption is that at this point you have worked through the Getting-Started vignette. If that is not the case, I would highly suggest starting there and then coming back here once you're familiar with the standard use cases of bakR. The topics to be addressed are as follows:

1. Performing differential synthesis analysis with bakR (and DESeq2, as you will see)
1. Comparing experimental samples (so going beyond bakR's comparison of a single reference sample to a collection of experimental samples).
1. Analyzing away-from-steady-state systems with bakR

These are the packages (or collection of packages) you are going to have to install and load in order to do everything presented in this vignette:

```{r setup}
library(bakR)

# Packages that are not automatically installed when bakR is installed
library(DESeq2)
library(pheatmap)

# Packages which are installed when bakR is installed
library(dplyr) 
library(magrittr) 
library(ggplot) 
```

## Differential synthesis analysis with bakR + DESeq2

## Performing additional comparisons

## Going beyond the steady-state assumption

